### 2012-05-11 trunk/paper-iswc-reification/dis.tex
made the whole thing compile

\section{Discussion}
What are benefits compared to RDF reification and other related work:
Compact Representation 
Efficient Querying 
 # Who bought Sybase and where did we get that fact?

@@

# Explicit bind of statement on variable for multiple joins.

>>>>

\section{Discussion}
What are benefits compared to RDF reification and other related work:
Compact Representation 
Efficient Querying 
 \# Who bought Sybase and where did we get that fact?

@@

\# Explicit bind of statement on variable for multiple joins.
